Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-02-13 joss/paper.rmd
tests manual brakcets

The growth of programming in the sciences has been explosive in the
last decade. This has facilitated the rapid advancement of science
through the agile development of computational tools. However,
concerns have begun to surface about the reproducibility of scientific
research in general @Baker2016 and the potential issues stemming from
issues with analytical software @Stodden2018. Specifically, there is a
growing recognition across disciplines that simply making data and
software "available" is not enough and that there is a need to improve
the transparency and stability of scientific software @Pasquier2018.

>>>>

The growth of programming in the sciences has been explosive in the
last decade. This has facilitated the rapid advancement of science
through the agile development of computational tools. However,
concerns have begun to surface about the reproducibility of scientific
research in general [@Baker2016] and the potential issues stemming from
issues with analytical software @Stodden2018. Specifically, there is a
growing recognition across disciplines that simply making data and
software "available" is not enough and that there is a need to improve
the transparency and stability of scientific software @Pasquier2018.
